Capture and Replay Tools in the Field

### 2017-04-27 paper.tex
Modified section - Extension and Modification of Reanimator. Added placeholders for some future sections.

\documentclass[12pt,journal]{IEEEtran}
\usepackage[
backend=biber,
style=numeric,
citestyle=numeric]{biblatex}
\addbibresource{citations.bib}
\usepackage{pifont}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{wrapfig,booktabs}
\usepackage{authblk}
\captionsetup{justification=raggedright,singlelinecheck=false}
\providecommand{\keywords}[1]{\textbf{Keywords} #1}
\begin{document}
\title{Capture and Replay Tools in the Field}
\author[1]{Deepa Chhetri}
\author[1]{Brian Pollack}
\affil[1]{Department of Electrical Engineering and Computer Science, Case Western Reserve University}
\maketitle

@@

\IEEEPARstart{S}{oftware} testing is a process of  evaluating the software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results. It involves the execution of a software component or system component to evaluate one or more properties of interest. Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{Nedyalkova:2013:OSC:2494444.2494464}. It not only involves testing the GUI but also the functionality of system. But manual testing GUI is tedious and time consuming. GUI capture and replay tools was  developed as a mechanism for testing the correctness of interactive applications with graphical user interfaces. Using a capture and replay tool, a tester can run an application and record the entire interactive session. The tool records all the user's events, such as the keys pressed or the mouse movements, in a log file called test scripts. Given tets scripts, the tool can then automatically replay the exact same interactive session any number of times without requiring a human user. This helps in early detection of bugs that might lead to system failure and therefore speed up the process of development.\\
The advantages of using capture and replay tools is that it saves time by making the process easy and quick. They save the time of hand-coding test scripts. They also make it simple for testers without significant programming skills to automate their test case \cite{McMaster:2009:EHF:1547559.1548260}. However, these tools also have some drawbacks. They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.\\
In this paper we compare four capture and replay tools on different criteria. This comparison study will be helpful for the developers to choose the capture and replay tool that would be best fit for testing their applications. Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.\\
 The remainder of this paper is organized as follows. Section 2 discusses about the previous work done in this field, Section 3 discusses about the tools that were used for the comparison, Section 4 decribes the evaluation criteria used to establish the comparison, Section 5 includes analysis of comparison, Section 6 describes in detail about the extension of Reanimator. Finally, in Section 7 we concluded the paper by presenting a short summary.

\section{Literature Review}
Nedyalkova and  Bernardino established a comparison of capture and replay tools. They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder. The criteria that they used for comparison is divided into two major groups - "General Characteristics'' and "Capture/Replay Characteristics''. General characteristics include:
\begin{enumerate}
\item Easy to Install
\item User Interface
\item Easy to Use
\item Easy to Launch Application Under Test (AUT)
\item Documentation
\item Tutorials
\item Examples
\item Programming Skills Required
\end{enumerate}
Capture/Replay Characteristics include:
\begin{enumerate}
\item Text Field - interaction with a JTextField
\item Mouse Move - detection of mouse movements on a component
\item Mouse Drag - detection of mouse drags
\item Mouse Clicks - detection of mouse clicks
\item Component - interaction with a window
\item Scrolling - interaction with the scrollbar of a JTextArea
\item File Dialog - navigating the directories in a JFileChooser
\item Combo Box - selecting an item in a JComboBox
\end{enumerate}
Based on the results, they found out that Jacareto is the best tool among all five evaluated. Jacareto is easy to install, had better documentation, does not require additional programming skills, supports all capture and replay characteristics except for navigation of dialog box. It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.

@@

@@

\section{Evaluation of Existing Tools}
 The four tools discussed in previous section are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8. We installed the tools Sahi, Telerik and Selenium. The code for Reanimator was directly deployed on a web server we manage. Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript is deployed at 1.eecs493.pollack.tech/index1.html. Reanimator demo comes with a tile game. We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.\\
The following criteria are used to establish comparison between these tools:\\ \\
\textbf{ \textit{Evaluation for ease of deployment:}}
\begin{enumerate}
\item Easy to install
\item Time required to install
\item User interface
\item Tutorials available
\item Open source
\item Programming skills required
\item Documentation provided
\item Examples provided
\item User interface for developers\\
\end{enumerate}
\textbf{\textit{Evalution for level of detail of measurements:}}
\begin{enumerate}
\item Interaction with text fields
\item Mouse movements
\item Mouse clicks
\item Mouse drags
\item Scrolling
\item Dialog box\\
\end{enumerate}
\textbf{\textit{Additional system information:}}
\begin{enumerate}
\item Size
\item Platforms
\item Browser support
\item Additional features\\
\end{enumerate}

@@

\section{Comparison Analysis}
The tools used here does their work of capturing and replaying the interactive sessions. But while taking other criteria into consideration, Sahi performs better than the other tools. Compared to Telerik and Reanimator, Sahi has easier installation. It has strong documentation available online. It does not require any programming skill to use Sahi. Sahi supports Chrome, Firefox and Internet Explorer. Selenium is easiest to install as it comes as firefox plugin. It also provides all the features like Sahi but the greatest setback of selenium is that it can only be used to capture and replay Firefox sessions. It has a great feature that allows the user to set speed to analyse the scenarios. No other tool provides this feature and has their own replay speed. This makes the process of analysis cumbersome if the default speed is very fast or slow. Telerik has a major setback that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective. It requires large hard disk space. It has the feature called visual storyboard which gives the snapshot of each scenario recorded by tool. This allows the developer to go to any snapshot. We used the one month free trial version of Telerik and requires to purchase once the trial period expires. Telerik also supports Chrome, Firefox and Internet Explorer. Reanimator is a small capture and replay tool inspired by Mugshot. It requires programming skills since it does not come as ready to use testing tool. It is built on JQuery 1.8.3. It requires programming skills to get Reanimator working.Also it works only on Firefox and Internet Explorer. It does not have any additional feauture. \\
We modified Reanimator by upgrading it to JQuery 3.2.0 and enabled it to work on Chrome too. It could be seen that the old version of Reanimator provided by the developers which is available at 1.eecs493.pollack.tech does not work on Chrome. While the modified version does work on Chrome. Reanimator comes with a demo which is a tile game. We have used the same game to test the modified version.
 Based on the evalution criteria seen in table 1, 2 and 3, we choose Sahi as the best tool among all others.

\section{Extension and Modification of Reanimator}
We forked the original Reanimator GitHub project at https://github.com/brianmpollack/reanimator. It took awhile to determine exactly how the original authors built Reanimator, but we were able to understand their work update their code to work with JQuery 3.2.0, the current version.

While updating the Reanimator code, we learned why it did not initially work in Google Chrome. It appears that the original authors tried to convert DOM objects to JSON. It is commonly known that JSON does not support circular references, but DOM objects contain numerous circular references. Some browsers, such as Firefox, will simply proceed with the JSON encoding and dropped the circular references, but other browsers, such as Chrome, will terminate the JavaScript process. We found a simple function that will remove the circular references from the DOM object and convert it to JSON, allowing Reanimator to now be used in any major browser. It needs testing on browsers such as Internet Explorer and Edge, but it worked in our preliminary tests with Firefox, Chrome, and Safari.

We also found a file error in the included demos. The original Makefile added a symbolic link to link the Reanimator JavaScript code to the demos, but the symbolic link caused issues both when all the code is uploaded to GitHub and even locally on my computer. For now, we simply copied the correct files into position on our web server, but we plan to update the Makefile to copy the files automatically. We are saving this for the end of the project because we anticipate having many changes to make to the demos (to reflect our new features/code), so we will update the demos all at once.

@@

%\bibliographystyle{IEEEtran}

>>>>

\documentclass[12pt,journal]{IEEEtran}
\usepackage[
backend=biber,
style=numeric,
citestyle=numeric]{biblatex}
\addbibresource{citations.bib}
\usepackage{pifont}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{wrapfig,booktabs}
\usepackage{authblk}
\usepackage{hyperref}
\captionsetup{justification=raggedright,singlelinecheck=false}
\providecommand{\keywords}[1]{\textbf{Keywords} #1}
\begin{document}
\title{Capture and Replay Tools in the Field}
\author[1]{Deepa Chhetri}
\author[1]{Brian Pollack}
\affil[1]{Department of Electrical Engineering and Computer Science, Case Western Reserve University}
\maketitle

@@

\IEEEPARstart{S}{oftware} testing is a process of  evaluating the software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results. It involves the execution of a software component or system component to evaluate one or more properties of interest. Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{Nedyalkova:2013:OSC:2494444.2494464}. It not only involves testing the GUI but also the functionality of system. But manual testing GUI is tedious and time consuming. GUI capture and replay tools was  developed as a mechanism for testing the correctness of interactive applications with graphical user interfaces. Using a capture and replay tool, a tester can run an application and record the entire interactive session. The tool records all the user's events, such as the keys pressed or the mouse movements, in a log file called test scripts. Given tets scripts, the tool can then automatically replay the exact same interactive session any number of times without requiring a human user. This helps in early detection of bugs that might lead to system failure and therefore speed up the process of development.
\par
The advantages of using capture and replay tools is that it saves time by making the process easy and quick. They save the time of hand-coding test scripts. They also make it simple for testers without significant programming skills to automate their test case \cite{McMaster:2009:EHF:1547559.1548260}. However, these tools also have some drawbacks. They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.
\par
In this paper we compare four capture and replay tools on different criteria. This comparison study will be helpful for the developers to choose the capture and replay tool that would be best fit for testing their applications. Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.
\par
The remainder of this paper is organized as follows. Section 2 discusses about the previous work done in this field, Section 3 discusses about the tools that were used for the comparison, Section 4 decribes the evaluation criteria used to establish the comparison, Section 5 includes analysis of comparison, Section 6 describes in detail about the extension of Reanimator. Finally, in Section 7 we concluded the paper by presenting a short summary.

\section{Literature Review}
Nedyalkova and  Bernardino established a comparison of capture and replay tools. They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder. The criteria that they used for comparison is divided into two major groups - "General Characteristics'' and "Capture/Replay Characteristics''. General characteristics include:
\begin{enumerate}
\item Easy to Install
\item User Interface
\item Easy to Use
\item Easy to Launch Application Under Test (AUT)
\item Documentation
\item Tutorials
\item Examples
\item Programming Skills Required
\end{enumerate}
Capture/Replay Characteristics include:
\begin{enumerate}
\item Text Field - interaction with a JTextField
\item Mouse Move - detection of mouse movements on a component
\item Mouse Drag - detection of mouse drags
\item Mouse Clicks - detection of mouse clicks
\item Component - interaction with a window
\item Scrolling - interaction with the scrollbar of a JTextArea
\item File Dialog - navigating the directories in a JFileChooser
\item Combo Box - selecting an item in a JComboBox
\end{enumerate}
Based on the results, they found out that Jacareto is the best tool among all five evaluated. Jacareto is easy to install, had better documentation, does not require additional programming skills, supports all capture and replay characteristics except for navigation of dialog box. It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.
\par

@@

\par

@@

\section{Evaluation of Existing Tools}
 The four tools discussed in previous section are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8. We installed the tools Sahi, Telerik and Selenium. The code for Reanimator was directly deployed on a web server we manage. Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript is deployed at 1.eecs493.pollack.tech/index1.html. Reanimator demo comes with a tile game. We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.
\par
The following criteria are used to establish comparison between these tools:\\ \\
\textbf{ \textit{Evaluation for ease of deployment:}}
\begin{enumerate}
\item Easy to install
\item Time required to install
\item User interface
\item Tutorials available
\item Open source
\item Programming skills required
\item Documentation provided
\item Examples provided
\item User interface for developers\\
\end{enumerate}
\textbf{\textit{Evalution for level of detail of measurements:}}
\begin{enumerate}
\item Interaction with text fields
\item Mouse movements
\item Mouse clicks
\item Mouse drags
\item Scrolling
\item Dialog box\\
\end{enumerate}
\textbf{\textit{Additional system information:}}
\begin{enumerate}
\item Size
\item Platforms
\item Browser support
\item Additional features\\
\end{enumerate}

@@

\section{Comparison Analysis}
The tools used here does their work of capturing and replaying the interactive sessions. But while taking other criteria into consideration, Sahi performs better than the other tools. Compared to Telerik and Reanimator, Sahi has easier installation. It has strong documentation available online. It does not require any programming skill to use Sahi. Sahi supports Chrome, Firefox and Internet Explorer. Selenium is easiest to install as it comes as firefox plugin. It also provides all the features like Sahi but the greatest setback of selenium is that it can only be used to capture and replay Firefox sessions. It has a great feature that allows the user to set speed to analyse the scenarios. No other tool provides this feature and has their own replay speed. This makes the process of analysis cumbersome if the default speed is very fast or slow. Telerik has a major setback that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective. It requires large hard disk space. It has the feature called visual storyboard which gives the snapshot of each scenario recorded by tool. This allows the developer to go to any snapshot. We used the one month free trial version of Telerik and requires to purchase once the trial period expires. Telerik also supports Chrome, Firefox and Internet Explorer. Reanimator is a small capture and replay tool inspired by Mugshot. It requires programming skills since it does not come as ready to use testing tool. It is built on JQuery 1.8.3. It requires programming skills to get Reanimator working.Also it works only on Firefox and Internet Explorer. It does not have any additional feauture.
\par
We modified Reanimator by upgrading it to JQuery 3.2.0 and enabled it to work on Chrome too. It could be seen that the old version of Reanimator provided by the developers which is available at 1.eecs493.pollack.tech does not work on Chrome. While the modified version does work on Chrome. Reanimator comes with a demo which is a tile game. We have used the same game to test the modified version.
 Based on the evalution criteria seen in table 1, 2 and 3, we choose Sahi as the best tool among all others.

\section{Extension and Modification of Reanimator}
We forked the original Reanimator GitHub project at \href{https://github.com/brianmpollack/reanimator}{https://github.com/brianmpollack/reanimator}. It took awhile to determine exactly how the original authors built Reanimator, but we were able to understand their work to determine how Reanimator was built.
\subsection{Original Reanimator Code}
Reanimator is built as an extension to JQuery and uses NodeJS to compile the source files. The compile scripts start with JQuery and use Almond to inject the Reanimator codebase. The main driver of Reanimator is contained in the lib/reanimator/core.js file. There is a file in the lib/reanimator/plugins directory which serves as the implementation for each logging feature that Reanimator supports.

\subsection{Issues with Original Code}
The original Reanimator code contained a few runtime and compilation issues, which we fixed before continuing to work with Reanimator.

\subsubsection{Google Chrome}
First, we observed that the precompiled code in the demos did not work in Google Chrome. It appears that the original authors tried to convert DOM objects to JSON. DOM stands for Document Object Model and JavaScript uses DOM Objects to represent the webpage contents.
\par
It is commonly known that JSON does not support circular references, but DOM Objects contain numerous circular references. Some browsers, such as Firefox, will simply proceed with the JSON encoding and will automatically drop the circular references, but other browsers, such as Chrome, will terminate the JavaScript process. We found a simple function that will remove the circular references from the DOM object while converting it to JSON, allowing Reanimator to now be used in any major browser (this fixed Reanimator in our tests with Chrome, Firefox, Safari, Internet Explorer, and Edge).

\subsubsection{File Link Error}
We also found a file error in the included demos. The original Makefile used a symbolic link to link the Reanimator JavaScript code to the demos, rather than copying the files. The symbolic link, however, caused issues both when the code is uploaded to GitHub and even when running locally.
\par
We updated the Makefile to copy the files into the demo folders. While we could have updated the demo code to link to the dist directory of the Reanimator code, we felt that it was important to allow the demos to be self-contained. This would allow a user to copy the contents of a demo folder directly to their server for testing.

\subsection{Uploading Log to Server}
Originally, Reanimator was not very useful to developers in the field. As soon as a user closed his or her browser, any recorded log would be destroyed. To make Reanimator more useful to developers, the main feature we wanted to add was log uploading.

\subsubsection{Client Side}

\subsubsection{Server Side}

\section{Future Additions to Reanimator}

\subsection{Developer Interface on Playback}

\subsection{Synchronize Only Changes}

\subsection{Smaller Upload Size}

@@
